### 2024-03-21 doc/15yrsChange.Rmd
added deer exclosure shp and figure 5 changes
figure updates & adding #s to results

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
# DISPLAY ITEMS
## I do not see any guidance as to the number of display items allowed in MEE.

#Tables
## example = 1

@@

@@

For the first time since the establishment of  the SCBI ForestGEO site, whole-plot aboveground C stocks decreased (Figure 2). From 2018 to 2023, whole-plot C stocks have decreased from **"X to X"** Mg C/ha. Both low-nuisance regions show similar decreases in C stocks going from **"X to X"** and **"X to X"** Mg C/ha, respectively. In the high deer high nuisance regions C stocks have decreased for the past two censuses, with a higher magnitude decrease of **"X to X"** Mg C/ha from 2018 to 2023. C stock decrease **is related to/ is explained by** above ground net biomass change. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes, but for the 2018 to 2023 interval there was a negative C flux of **VALUE** Mg C/ha/year (Figure 3a).

@@

![**Figure `r regen_failure`.**](display/Figure6.jpeg)

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
# DISPLAY ITEMS

#Tables

@@

```{r eval = TRUE, echo = FALSE, warning = FALSE, results = 'hide'}
library(tidyverse)
### Numbers for text
##load in text data
load("results-text/Figure2_textdata.Rdata")
load("results-text/Figure3_textdata.Rdata")
load("results-text/Figure4_textdata.Rdata")
load("results-text/Figure5_textdata.Rdata")

##Figure 2

#whole plot
wp_ABG_2018 <- figure2_agb  %>% filter(Year == "2018" & Group == "Whole Plot")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
wp_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "Whole Plot")  %>%  pull(Abg_C_Mg_Ha) %>% round(digits = 1)

#high deer, high canopy vulnerability
hdhn_ABG_2013 <- figure2_agb  %>% filter(Year == "2013" & Group == "3")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
hdhn_ABG_2018 <- figure2_agb  %>% filter(Year == "2018" & Group == "3")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
hdhn_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "3")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)

#low canopy vulnerability
ldlv_ABG_2018 <-  figure2_agb  %>% filter(Year == "2018" & Group == "1")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
ldlv_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "1")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
hdlv_ABG_2018 <-  figure2_agb  %>% filter(Year == "2018" & Group == "2")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1) 
hdlv_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "2")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)

@@

For the first time since the establishment of  the SCBI ForestGEO site, whole-plot aboveground C stocks decreased (Figure 2). From 2018 to 2023, whole-plot C stocks have decreased from `r wp_ABG_2018` to `r wp_ABG_2023` Mg C ha^-1^. In regions with  high deer density and high canopy vulnerability AGB decreased significantly over the past two censuses, from `r hdhn_ABG_2013` Mg C ha^-1^ in 2013, to `r hdhn_ABG_2018` Mg C ha^-1^ in 2018, and `r hdhn_ABG_2023` Mg C ha^-1^ in 2023. Areas with low density of vulnerable canopy species experienced minor decreases in AGB; C stocks inside and outside of the deer exclosure decreased from **"X to X"**  and **"X to X"** Mg C ha^-1^, respectively.  C stock decrease **is related to/ is explained by** above ground net biomass change. In the first two census intervals, 2008 to 2013 and 2013 to 2018, there were positive C fluxes, but for the 2018 to 2023 interval there was a negative C flux of **VALUE** Mg C/ha/year (Figure 3a).

@@

![**_Figure `r regen_failure`._**](display/Figure6.jpeg)
